The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-08-29 paper/mnras/paper.tex
Updating

%%% MNRAS stuff  %%%
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols

@@

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.  Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively.  From this point onwards metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.

@@

@@

To explore plausible binary detection scenarios, we adopt a parametrized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
\cite{2016arXiv160508783L} and others.

@@

>>>>

%%% MNRAS stuff  %%%
%\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols

@@

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively. {\bf Richard:
 We adopt a fiducial Salpeter IMF.   We do not
 self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
 practice, our model for chemical evolution is derived from isolated stars.  
 As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
 procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
 In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
 including  phenomenological models for cosmological
 metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
 the mass-metallicity-SFR correlation
 \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
 consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
 \cite{2015MNRAS.452L..36D}; see YYY for comparison.
}

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.   Once created,  metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.  
{\bf Combined with infall, this procedure produces a range of metallicities within each galaxy.  
}

@@

\subsection{Mass-metallicity-SFR relation}

{\bf

Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
\begin{eqnarray}
12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
\end{eqnarray}
In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
star formation rate can occur only at low metallicity.  
Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
diagnostic.  ARE THEY REASONABLE?

}

@@

To explore plausible binary detection scenarios, we adopt a parametrized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
\cite{2016arXiv160508783L} and others.
{\bf 
Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
distinct, special group of low-metallicity Population III stars.
}

@@

{\bf In our investigation, we have neglected the impact of population III stars.
Previous studies suggest the first generation of stars may contribute a small but nonzero fraction of detectable events,
potentially with distinctively high black hole masses
\cite{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
% http://adsabs.harvard.edu/abs/2004ApJ...612..597W
}

### 2016-08-29 paper/paper.tex
paper
paper.tex: add reminder with DCC number
add Fabio Governato to author list
add author
add Sijing
Updating

\begin{document}
%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
\title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
\author{R.\ O'Shaughnessy}
\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
\email{oshaughn@mail.rit.edu}
\author{ J. Bellovary}
\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
\email{jbellovary@qcc.cuny.edu}

@@

\end{abstract}
% DCC: 
% arxiv:
% DOI:

@@

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.  Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively.  From this point onwards metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.

@@

We include two additional Milky Way simulations with similar $z = 0$ properties, which have evolutionary histories that fall in between the extremes of the two described above.  The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
\msun$, and maximum circular velocity $v_{\rm circ} = 250$ km s$^{-1}$.  The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.  These galaxies are also described \citet{Munshi13,Bellovary14}.

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/dwarf1}
\includegraphics[width=\columnwidth]{Figures/dwarf1}
\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
\label{fig:dwarfimages}
}
\end{figure*}

>>>>

\begin{document}
%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
\title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
\author{R.\ O'Shaughnessy}
\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
\email{oshaughn@mail.rit.edu}
\author{ J. Bellovary}
\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
\email{jbellovary@qcc.cuny.edu}
\author{C. Christensen}
\affiliation{Department of Physics, Grinnell College, Grinnell, IA, 50112}
\author{ F. Governato}
\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98195}
\author{ S. Shen}
\affiliation{Cambridge or maybe Oslo}

%\email{fabio@astro.washington.edu}

@@

\end{abstract}
% DCC:   P1600229
% arxiv:
% DOI:

@@

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively.  {\bf Richard:
 We adopt a fiducial Salpeter IMF.  We do not introduce a special group of Population III stars (??).
 As described in ZZZ, the  derived cosmological metal evolution and star formation rate history derived using this
 procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
 In particular, our procedure is broadly consistent with one of the \cite{2016MNRAS.461.3877D} models
}

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.   Once created,  metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.

@@

We include two additional Milky Way simulations with similar $z = 0$ properties, which have evolutionary histories that fall in between the extremes of the two described above.  The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
\msun$, and maximum circular velocity $v_{\rm circ} = 250$ km s$^{-1}$.  The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.  These galaxies are also described in \citet{Munshi13,Bellovary14}.

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/dwarf1}
\includegraphics[width=\columnwidth]{Figures/h516}
\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
\label{fig:dwarfimages}
}
\end{figure*}
